Meaning of simple rules in investment strategies of algorithmic trading

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
The following sketches from a) to d) show
This $m$ value

\indent The following sketches from a) to d) shows the change in the market against a particular average from $C^d_{m_{i}}$ to $C^a_{m_{i}}$.\\

@@

\indent So $m_{a}$ is the parameter learned on a particular section of a time series. This m value,for which achieves a maximum gain of opened positions (for quarter a) long). On another length of time series, by (6) it could have different value. Similarly, for the parameters $m_{b}$, $m_{c}$ and $m_{d}$.\\

>>>>

\indent The following sketches from a) to d) show the change in the market against a particular average from $C^d_{m_{i}}$ to $C^a_{m_{i}}$.\\

@@

\indent So $m_{a}$ is the parameter learned on a particular section of a time series. This $m$ value,for which achieves a maximum gain of opened positions (for quarter a) long). On another length of time series, by (6) it could have different value. Similarly, for the parameters $m_{b}$, $m_{c}$ and $m_{d}$.\\
